SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-07-06 scipy-1.0/scipy-optimize.tex
Adds references to trust-* paragraph

In recent SciPy versions, four new methods for unconstrained optimization have been added to \texttt{minimize}: \texttt{dogleg}, \texttt{trust-ncg}, \texttt{trust-exact}, and \texttt{trust-krylov}. All are trust-region methods that build a local model of the objective function based on first and second derivative information, approximate the best point within a local ``trust region'', and iterate until a local minimum of the original objective function is reached, but each has unique characteristics that make it appropriate for certain types of problems. For instance, \texttt{trust-exact} achieves fast convergence by solving the trust-region subproblem almost exactly, but it requires the second derivative Hessian matrix to be stored and factored every iteration, which may preclude the solution of large problems ($\geq 1000$ variables). On the other hand, \texttt{trust-ncg} and \texttt{trust-krylov} are well-suited to large-scale optimization problems because they do not need to store and factor the Hessian explicitly, instead using second derivative information in a faster, approximate way.

>>>>

In recent SciPy versions, four new methods for unconstrained optimization have been added to \texttt{minimize}: \texttt{dogleg}\cite{powell_new_1970, nocedal_numerical_2006}, \texttt{trust-ncg}\cite{steihaug_conjugate_1983, nocedal_numerical_2006}, \texttt{trust-exact}\cite{conn_trust_2000, more_computing_1983}, and \texttt{trust-krylov}\cite{gould_solving_1999, lenders_trlib:_2016}. All are trust-region methods that build a local model of the objective function based on first and second derivative information, approximate the best point within a local ``trust region'', and iterate until a local minimum of the original objective function is reached, but each has unique characteristics that make it appropriate for certain types of problems. For instance, \texttt{trust-exact} achieves fast convergence by solving the trust-region subproblem almost exactly, but it requires the second derivative Hessian matrix to be stored and factored every iteration, which may preclude the solution of large problems ($\geq 1000$ variables). On the other hand, \texttt{trust-ncg} and \texttt{trust-krylov} are well-suited to large-scale optimization problems because they do not need to store and factor the Hessian explicitly, instead using second derivative information in a faster, approximate way.
